### 2021-02-26 README.Rmd
Update readme

```{r}
london_zones = zb_zone(london_c(), london_a())
zb_plot(london_zones)
```

@@

```{r fig.height=3}
par(mfrow=c(1,3))
zb_plot(zb_doughnut(london_c(), london_a(), n_circles = 5), title = "Doughnuts")
zb_plot(zb_segment(london_c(), n_segments = 20), title = "Segments")
zb_plot(zb_zone(london_c(), n_circles = 4, n_segments = 4), title = "4 segments, 4 circles")
```

>>>>

```{r}
london_zones <- zb_zone(london_c(), london_a())
zb_plot(london_zones)
```

@@

```{r fig.height=3}
par(mfrow = c(1, 3))
zb_plot(zb_doughnut(london_c(), london_a(), n_circles = 5), title = "Doughnuts")
zb_plot(zb_segment(london_c(), n_segments = 20), title = "Segments")
zb_plot(zb_zone(london_c(), n_circles = 4, n_segments = 4), title = "4 segments, 4 circles")
```

## Contribute

Contributions are welcome!

It may be worth checking-in in a [discussion post](https://github.com/zonebuilders/zonebuilder/discussions/28) before opening an issue.

## Citation

Watch this space.
